---
title: "inovick_OriginalHomeworkCode_02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Challenge 1: What is the probability that she will hear more than 8 calls during any given session?
```{r}
?dpois #to give me more information on the Poisson Distribution

x<-8
l<-15
1-ppois(q=x,lambda=l) 
#Probability=0.9625535 or 96%
```

## Challenge 2: What is the probability that she will hear no calls in a session?

```{r}
dpois(0,15)
#Probability=3.059023e-07
```
## Challenge 3: What is the probability that she will hear exactly 3 calls in a session?
```{r}
dpois(3,15)
#Probability=0.0001720701
```
## Challenge 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30
```{r}
x<-0:30
l=15
barplot(dpois(x,l))
```
## Challenge 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions). 
```{r}
rpois(104,15) #simulated 104 results from this distribution
```
## Challenge 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r}
y<-rpois(104,15)
hist(y,xlim=c(0,30),xlab="Number of Calls",main="Call Monitoring Histogram",breaks=30,col="chartreuse")
```

